### 2022-10-16 manuscript.Rmd
Enable fitting control models independently

```{r, mixed_models, include=FALSE}
# Construct model formula
form <- ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

@@

  # Filter relevant conditions for the main analysis
  trials %>%
    mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
    drop_na() -> trials_main

  # Actually fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
    set_names(deps) -> models

@@

```{r, control_analysis, include=FALSE}
# (Re-)do the actual model fitting if requested
if (run$control_analysis) {

  # Filter relevant conditions for the control analysis
  conditions_control <- c("Informed", "Exclude_informed")
  trials %>%
    mutate(condition = factor(condition, levels = conditions_control)) %>%
    drop_na() -> trials_control

@@

>>>>

```{r, mixed_models, include=FALSE}
# Filter relevant conditions for the main analysis
trials %>%
  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
  drop_na() -> trials_main

# Construct model formula
form <- ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

@@

  # Fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
    set_names(deps) -> models

@@

```{r, control_analysis, include=FALSE}
  # Filter relevant conditions for the control analysis
  conditions_control <- c("Informed", "Exclude_informed")
  trials %>%
    mutate(condition = factor(condition, levels = conditions_control)) %>%
    drop_na() -> trials_control

@@

# (Re-)do the actual model fitting if requested
if (run$control_analysis) {
